KidsAIR initial home/child data work

### 2020-05-12 demographics_summary.Rmd
demographics/id filtering and merging

---
title: 'KidsAIR: household demographics summary'
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 25 March 2020"
output:
  beamer_presentation: default
  powerpoint_presentation: default
---

@@

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_clean <- read_rds(paste0(file_path, "Output/demographics_clean.rds")) 
pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```

>>>>

---
title: 'KidsAIR: household demographics summary'
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 12 May 2020"
output:
  beamer_presentation: default
  powerpoint_presentation: default
---

@@

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_initial <- read_rds(paste0(file_path, "Output/demographics_clean.rds")) 
pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```

```{r}
# number of placebo households, total and by area
placebo_homes <- kids_linked_ids %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  count(area)

# number of placebo households, total and by area
treatment_homes <- kids_linked_ids %>% 
  filter(winter_id == 1) %>% 
  count(treatment)

# number of placebo households, total and by area
treatment_kids <- demographics_initial %>% 
  filter(winter_id == 2) %>% 
  count(treatment)
```

```{r}
# add new vars to dataset

```

```{r}
# summary data for manuscript tables
demo_funct_total <- function(var, data = demographics_clean){

demographics_summary <- demographics_clean %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent)
demographics_summary
}

demo_funct_total("gender_parent")

demo_funct_area <- function(var, data = demographics_clean){

demographics_summary <- demographics_clean %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(area, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent)
demographics_summary
}

demo_funct_area("gender_parent")
```

### 2020-05-12 home_child_data_cleaning.Rmd
demographics/id filtering and merging

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 11 May 2020"
output: pdf_document
---

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > Home Data > parentdemographics.xlsx
wmt_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/WMT/wmt_parent_demographics_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- wmt_homewinter_initial %>% 
  left_join(wmt_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(wmt_home_initial, by = "home_id") %>% 
  left_join(wmt_child_initial, by = "home_id") %>% 
  mutate(area = "WMT") %>% 
  filter(!is.na(enrolled))

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > homewinter.xlsx
nn_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homewinter_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > Home Data > parentdemographics.xlsx
nn_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/NN/nn_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- nn_homewinter_initial %>% 
  left_join(nn_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(nn_home_initial, by = "home_id") %>% 
  left_join(nn_child_initial, by = "home_id") %>% 
  mutate(area = "NN") %>% 
  filter(!is.na(enrolled))

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > Home Data > parentdemographics.xlsx
ak_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/AK/ak_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- ak_homewinter_initial %>% 
  left_join(ak_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(ak_home_initial, by = "home_id") %>% 
  left_join(ak_child_initial, by = "home_id") %>% 
  mutate(area = "AK") %>% 
  filter(!is.na(enrolled))

@@

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids)

#write_rds(kids_ids, paste0(file_path, "Output/kids_linked_ids.rds")

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds")) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = if_else(home == "CH218", winter_id + 1, winter_id)) %>% 
  filter(winter_id == 1 | winter_id == 2)

#write_rds(kids_linked_ids, paste0(file_path, "Output/kids_linked_ids.rds"))
```

@@

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics)

# write_rds(kids_demographics, paste0(file_path, "Output/kids_combined_demographics.rds"))

kids_demographics <- read_rds(paste0(file_path, "Output/kids_combined_demographics.rds"))
```

# Clean demographics data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_demographics <- read_rds(paste0(file_path, "Output/kids_combined_demographics.rds"))

demographics_clean <- kids_demographics %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash) %>% 
  mutate(home_winter_id = as.numeric(home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 1, 77, home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 2, 111, home_winter_id),
         home_winter_id = as.factor(home_winter_id)) %>% 
  filter(winter_id == 1 | winter_id == 2)

# write_rds(demographics_clean, paste0(file_path, "Output/demographics_clean.rds"))
```

>>>>

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 12 May 2020"
output: pdf_document
---

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > Home Data > parentdemographics.xlsx
wmt_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/WMT/wmt_parent_demographics_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- wmt_homewinter_initial %>% 
  full_join(wmt_parent_demographics_initial, by = "home_winter_id") %>% 
  #mutate(home_id = if_else(home_winter_id == 275, "153", home_id)) %>% 
  ### 1st big filter - remove those with no home_id
  ### All other past this point should be considered "enrolled"
  filter(!is.na(home_id)) %>% 
  full_join(wmt_home_initial, by = "home_id") %>% 
  full_join(wmt_child_initial, by = "home_id") %>% 
  filter(!is.na(home_winter_id)) %>% 
  mutate(area = "WMT") 
  ### Once data is joined for all areas, filter for homes with treatment assignment
  ### This will help further refine data for analysis and be a number in the flow chart

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > homewinter.xlsx
nn_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homewinter_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = if_else(home_id == 62 | home_id == 45, winter_id + 1, winter_id),
         winter_id = as.character(winter_id)) %>% 
  filter(winter_id == 1 | winter_id ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > Home Data > parentdemographics.xlsx
nn_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/NN/nn_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- nn_homewinter_initial %>% 
  full_join(nn_parent_demographics_initial, by = "home_winter_id") %>% 
  ### 1st big filter - remove those with no home_id
  ### All other past this point should be considered "enrolled"
  filter(!is.na(home_id)) %>% 
  full_join(nn_home_initial, by = "home_id") %>% 
  full_join(nn_child_initial, by = "home_id") %>% 
  mutate(area = "NN") 
  ### Once data is joined for all areas, filter for homes with treatment assignment
  ### This will help further refine data for analysis and be a number in the flow chart

@@

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > Home Data > parentdemographics.xlsx
ak_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/AK/ak_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

# join all files from above
joined1 <- ak_homewinter_initial %>% 
  full_join(ak_parent_demographics_initial, by = "home_winter_id") %>% 
  ### 1st big filter - remove those with no home_id
  ### All other past this point should be considered "enrolled"
  filter(!is.na(home_id)) %>% 
  full_join(ak_home_initial, by = "home_id") %>% 
  full_join(ak_child_initial, by = "home_id") %>% 
  mutate(area = "AK") 
  ### Once data is joined for all areas, filter for homes with treatment assignment
  ### This will help further refine data for analysis and be a number in the flow chart

@@

# Count total observations in dataset for homes and kids
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # distinct homes in database = 360
  filter(!is.na(child_id_num)) %>% 
  # distinct(area, child_id_num, .keep_all = TRUE) %>%  # distinct kids in database = 512
  # distinct(area, home_id, .keep_all = TRUE) %>% # distinct homes with kids in databse = 340
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(!is.na(treatment)) %>%  
  distinct(area, child_id_num, .keep_all = TRUE) %>%   # distinct kids with treatment = 512
  distinct(area, home_id, .keep_all = TRUE)  # distinct homes with kids with treatment = 340
```

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%  
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # enrolled homes in database = 360
  filter(!is.na(treatment)) %>% 
  # distinct(area, home_id)  # randomized homes with treatment assignment = 342
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>% 
  #distinct(area, home_id)  # randomized homes with treatment assignment = 340
  ungroup() %>% 
  arrange(area, home)

write_rds(kids_ids, paste0(file_path, "Output/kids_linked_ids.rds"))
```

@@

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  filter(!is.na(child_id_num)) %>% 
  filter(!is.na(treatment)) %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash) %>% 
  ungroup() %>% 
  arrange(area, home, child_id_char)

write_rds(kids_demographics, paste0(file_path, "Output/kids_combined_demographics.rds"))
```
